### 2024-08-07 cluster-analysis.qmd
20240807 - error code

numTiersRB <- 3

# The following code errors out:
#tiersRB_boostrap <- mclustBootstrapLRT(
#  player_stats_seasonal_offense_recentRB$fantasy_points,
#  modelName = "V") # variable/unequal variance (for univariate data)
#
#numTiersRB <- as.numeric(summary(tiersRB_boostrap)[,"Length"][1]) # or could specify the number of teams manually
#
#tiersRB_boostrap
#plot(
#  tiersRB_boostrap,
#  G = numTiersRB - 1)
```

>>>>

numTiersRB <- 3
```

The model-based bootstrap clustering of Running Backs' fantasy points is unable to run due to an error:

```{r}
tiersRB_boostrap <- mclustBootstrapLRT(
  player_stats_seasonal_offense_recentRB$fantasy_points,
  modelName = "V") # variable/unequal variance (for univariate data)
```

Thus, we cannot use the following code, which would otherwise summarize the model results, specify the number of tiers, and plot model comparisons:

numTiersRB <- as.numeric(summary(tiersRB_boostrap)[,"Length"][1]) # or could specify the number of teams manually

tiersRB_boostrap
plot(
  tiersRB_boostrap,
  G = numTiersRB - 1)
```
